---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
```

# [Bet, Sweat, and Forget.](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY)

#### Each week during the NFL season, Ryan Brill and Nick Miller make $50 worth of NFL bets on the [Bet, Sweat, and Forget](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY) podcast, competing for glory and the title of "best bettor". Check out the podcast on Apple Podcasts and [Spotify](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY).

```{r, echo=FALSE, warning=FALSE}
# COLIN COWHERD'S BLAZIN 5
colins_W <- c(2,2,4,1,1,2,3,4,1,4,1,2,3,3,4,1,2)
colins_L <- c(3,3,1,3,4,3,2,1,4,1,4,2,2,2,1,3,3)
colins_P <- c(0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0)
M <- 110
colins_profits <- (colins_W * (100/M) - colins_L)*10
colins_cumulative_profits <- cumsum(colins_profits)
colins_final_record <- paste(sum(colins_W), sum(colins_L), sum(colins_P), sep = "-")
colins_final_profit <- paste0("-$", abs(round(colins_cumulative_profits[length(colins_cumulative_profits)],2)) )
```

```{r, echo=FALSE, warning=FALSE, fig.align = "center",fig.width=8.5, fig.height=5}
# out.width = "85%"
nick <- c(0,35.83, 115.17, 103.78, 153.77, 173.33, 177.37, 174.54, 124.54, 74.54, 62.72, 62.72, 62.72, 85.53, 52.49, 52.49, 69.76, 75.34, NA)
ryan <- c(0,-7.09, -9.49, -1.02, 36.22, 31.47, 5.33, 61.17, 53.19, 47.2, 32.29, 19.32, 42.88, 44.86, 13.56, 13.56, -20.31, -14.97, 2.09)
colin <- c(0, colins_cumulative_profits, NA)
guest_profits <- c(NA,NA, 20.74, -30.91, NA,NA,NA, -23.69, -50, -41, -21.36, -40, -23.73, -7.51, 19.27, -50, NA, -50)
guest_names <- c(NA,NA,"Harrison", "Griffin", NA,NA,NA, "Vaish", "Kole", "Adil", "Jake", "Aaron", "Griffin", "Griffin", "Griffin", "Bernie",NA, "Jerry")
guest_weeks <- c(0:9, 10, 10, 11:16)

N = length(ryan)
num_weeks <- 0:(N-1)
df <- data.frame(nick, ryan, colin, num_weeks)
df_guests <- data.frame(guest_profits, guest_names, guest_weeks)

ggplot(data = df) +
  
geom_line(aes(x = df$num_weeks, y = df$colin, color = "Colin Cowherd's Blazin' 5**")) +
geom_line(aes(x = df$num_weeks, y = df$nick, color = "Nick")) +
geom_line(aes(x = df$num_weeks, y = df$ryan, color = "Ryan")) +
geom_line(aes(x = df$num_weeks, y = rep(0, N), color = "Zero")) +
  
geom_point(data = df_guests, aes(x= df_guests$guest_weeks, y = df_guests$guest_profits, color = "Guest")) +
geom_text(data = df_guests, aes(x= df_guests$guest_weeks, y = df_guests$guest_profits, label=guest_names, color = "Guest"),hjust=0, vjust=0) +
  
scale_color_manual(values=c("chartreuse3","gray25", "firebrick", "dodgerblue2", "gray65")) +
labs(title = "Bet, Sweat, and Forget 2020 NFL Betting Results", x = "NFL Week Number", y = "Cumulative Profit, USD", color="") +
scale_x_continuous(breaks = num_weeks) +
scale_y_continuous(breaks = c(-50,0,50,100,150)) +
expand_limits(x = N, y = 0)
```

### Check out the details of our weekly bets [<u>here</u>](https://docs.google.com/spreadsheets/d/13TNrDf-RFrJfA36LXjcGHZ5fr_W4pD1yO2_RyniTxww/edit?usp=sharing).

### [Are Ryan Brill and Nick Miller better at sports betting than a monkey?](https://ryansbrill.com/ryan_vs_monkey/)

_\*\*Colin Cowherd's 2020 Blazin' 5 cumulative profit is calculated by placing $10 on each of his 5 weekly NFL pointspread bets, using a -110 moneyline for each bet. Colin's final record for the 2020 NFL season is `r colins_final_record`, which in our scheme translates to a final profit of `r colins_final_profit`, agreeing with the above graph. The math behind this is:_ 
```{r, comment=NA}
(40 * 100/110 - 42)*10
```
