---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
```

# [Bet, Sweat, and Forget.](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY)

#### Each week during the NFL season, Ryan Brill and Nick Miller make $50 worth of NFL bets on the [Bet, Sweat, and Forget](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY) podcast, competing for glory and the title of "best bettor". Check out the podcast on Apple Podcasts and [Spotify](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY).

## 2021 NFL Season.


```{r, echo=FALSE, warning=FALSE, fig.align = "center",fig.width=8.5, fig.height=5}
# out.width = "85%"
nick <- c(0,26.97,-23.03,20.53,37.08, 66.17, 50.99,0.99,-1.28,-51.28,-75.03,-88.28,-90.5,-119.42,-59.04)
ryan <- c(0,-7.83,17.82,37.92,55.16, 21.43, -28.57,16.97,-33.03,-33.03,-50.13,-39.27,-89.27,-89.48,-109.4)
Elon <- c(0, -7.79, -27.29,-28.99,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA)
#Shelon <- c(0, -23.2, -50.4,-37.9)
#Belon <- c(0,-50,-100,-87.5)
guest_profits <- c(NA,23.76, 17.40,43.59,-21.36,-50,NA,NA,-50,-50,16.82,NA,NA,NA,NA,NA)
guest_names <- c(NA,"Harry", "Griff", "Kole","Jake","Vaish",NA,NA,"Adil","Bernie","Frank",NA,NA,NA,NA,NA)
guest_weeks <- c(0,1,1,2,3,4,5,6,7,8,9,10,11,12,13,NA)

N = length(ryan)
num_weeks <- 0:(N-1)
df <- data.frame(nick, ryan, num_weeks, Elon)#, Shelon, Belon)

df_guests <- data.frame(guest_profits, guest_names, guest_weeks)

library(ggthemes)
theme_set(theme_classic())

COLORS <- c("nick" = "firebrick", 
            "ryan" = "dodgerblue2",
            "zero" = "gray50",
            "guest" = "gray25",
            "elon" = "mediumseagreen")#,
            # "shelon" = "darkseagreen3",
            # "belon" = "lightsteelblue2")

ggplot(data = df) +
  
geom_line(aes(x = df$num_weeks, y = df$Elon, color = "elon"), lwd=.4) +
#geom_line(aes(x = df$num_weeks, y = df$Shelon, color = "shelon"), lwd=.4) +
#geom_line(aes(x = df$num_weeks, y = df$Belon, color = "belon"), lwd=.4) +
geom_line(aes(x = df$num_weeks, y = rep(0, N), color = "zero"), lwd=.4) +
geom_line(aes(x = df$num_weeks, y = df$nick, color = "nick"), lwd=1.3) +
geom_line(aes(x = df$num_weeks, y = df$ryan, color = "ryan"), lwd=1.3) +

geom_point(data = df_guests, aes(x= df_guests$guest_weeks, 
                                 y = df_guests$guest_profits, 
                                 color = "guest")) +
geom_text(data = df_guests, aes(x= df_guests$guest_weeks, 
                                y = df_guests$guest_profits, 
                                label=guest_names, 
                                color = "guest"),
          hjust=0, vjust=0) +
  scale_color_manual(values=COLORS, name="legend") +
#scale_color_discrete(name = "",labels = c("wind", "temperature")) + 
#scale_color_manual(values=c( "gray25","firebrick", "dodgerblue2", "gray65", "green", "green", "green")) +
labs(title = "Bet, Sweat, and Forget 2021 NFL Betting Results", x = "NFL Week Number", y = "Cumulative Profit, USD", color="") +
scale_x_continuous(breaks = num_weeks) +
scale_y_continuous(breaks = seq(-90,90,by=10)) +
expand_limits(x = N, y = 0)
```



#### View our weekly bets, and the detailed accounting, [here.](https://docs.google.com/spreadsheets/d/1IU1Dw72FoYQJVTqJl-prHRBDOvDPqIjvmUKVmu3dCXQ/edit#gid=0)

#### View previous seasons of the Bet, Sweat, and Forget Podcast [here.](/bsf/bsf_prev_szns/)
