---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
```

# [Bet, Sweat, and Forget.](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY)

#### Each week during the NFL season, Ryan Brill and Nick Miller make $50 worth of NFL bets on the [Bet, Sweat, and Forget](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY) podcast, competing for glory and the title of "best bettor". Check out the podcast on Apple Podcasts and [Spotify](https://open.spotify.com/show/1bABVhkwnd3sDaBSZLC0oY).

## 2021 NFL Season.

<!--
```{r, echo=FALSE, warning=FALSE, fig.align = "center",fig.width=8.5, fig.height=5}
# out.width = "85%"
nick <- c(0,35.83, 115.17, 103.78, 153.77, 173.33, 177.37, 174.54, 124.54, 74.54, 62.72, 62.72, 62.72, 85.53, 52.49, 52.49, 69.76, 75.34, 64.64, 59.32, 37.96, 27.06)
ryan <- c(0,-7.09, -9.49, -1.02, 36.22, 31.47, 5.33, 61.17, 53.19, 47.2, 32.29, 19.32, 42.88, 44.86, 13.56, 13.56, -20.31, -14.97, 2.09, -19.87, -42.72, -92.72)
guest_profits <- c(NA,NA, 20.74, -30.91, NA,NA,NA, -23.69, -50, -41, -21.36, -40, -23.73, -7.51, 19.27, -50, NA, -50,NA,NA,-30.91,38.3,-50,-17)
guest_names <- c(NA,NA,"Harry", "Griffin", NA,NA,NA, "Vaish", "Kole", "Adil", "Jake", "Aaron", "Griffin", "Griffin", "Griffin", "Bernie",NA, "Jerry",NA,NA,"Kole","Harry","Harry","Griff")
guest_weeks <- c(0:9, 10,10, 11:20, 21,21)

N = length(ryan)
num_weeks <- 0:(N-1)
df <- data.frame(nick, ryan, num_weeks)

df_guests <- data.frame(guest_profits, guest_names, guest_weeks)

ggplot(data = df) +
  
geom_line(aes(x = df$num_weeks, y = df$nick, color = "Nick")) +
geom_line(aes(x = df$num_weeks, y = df$ryan, color = "Ryan")) +
geom_line(aes(x = df$num_weeks, y = rep(0, N), color = "Zero")) +
  
geom_point(data = df_guests, aes(x= df_guests$guest_weeks, y = df_guests$guest_profits, color = "Guest")) +
geom_text(data = df_guests, aes(x= df_guests$guest_weeks, y = df_guests$guest_profits, label=guest_names, color = "Guest"),hjust=0, vjust=0) +
  
scale_color_manual(values=c("chartreuse3","gray25", "firebrick", "dodgerblue2", "gray65")) +
labs(title = "Bet, Sweat, and Forget 2020 NFL Betting Results", x = "NFL Week Number", y = "Cumulative Profit, USD", color="") +
scale_x_continuous(breaks = num_weeks) +
scale_y_continuous(breaks = c(-50,0,50,100,150)) +
expand_limits(x = N, y = 0)
```
--->


#### View our weekly bets, and the detailed accounting, [here.](https://docs.google.com/spreadsheets/d/1IU1Dw72FoYQJVTqJl-prHRBDOvDPqIjvmUKVmu3dCXQ/edit#gid=0)

#### View previous seasons of the Bet, Sweat, and Forget Podcast [here.](https://ryansbrill.com/bsf/bsf_prev_szns/)
